ECCCos from the Black Box:\\ Faithful Explanations through\\ Energy-Constrained Conformal Counterfactuals

### 2023-09-26 paper/body.tex
done

For the predictive modelling tasks, we use multi-layer perceptrons (\textit{MLP}), deep ensembles, joint energy models (\textit{JEM}) and convolutional neural networks (LeNet-5 \textit{CNN}). Both joint-energy modelling and ensembling have been associated with improved generative properties and adversarial robustness~\citep{grathwohl2020your,lakshminarayanan2016simple}, so we expect this to be positively correlated with the plausibility of \textit{ECCCo}. To account for stochasticity, we generate multiple counterfactuals for each target class, generator, model and dataset. Full details concerning our parameter choices, training procedures and model performance can be found in the appendix.

>>>>

For the predictive modelling tasks, we use multi-layer perceptrons (\textit{MLP}), deep ensembles, joint energy models (\textit{JEM}) and convolutional neural networks (LeNet-5 \textit{CNN}~\citep{lecun1998gradient}). Both joint-energy modelling and ensembling have been associated with improved generative properties and adversarial robustness~\citep{grathwohl2020your,lakshminarayanan2016simple}, so we expect this to be positively correlated with the plausibility of \textit{ECCCo}. To account for stochasticity, we generate multiple counterfactuals for each target class, generator, model and dataset. Full details concerning our parameter choices, training procedures and model performance can be found in the appendix.
